Handling String-Number Conversion in String Constraint Solving

### 2019-11-11 evaluation.tex
evalutaion: update tables

\begin{table*}[t]
\centering
\caption{Results of z3-Trau, cvc4, and z3 on string benchmarks}
\begin{tabular}{l | r r r | r r r | r r r | r r r}
\hline
\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{z3-str3} \\
			& sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ \\ \hline
PyEx		& 19655 & 3851 & 1915/0 & 19763 & 3834 & 0/1824 & 16578 & 3832 & 5011/0 & 3023 & 3835 & 16717/1846 \\ 
APLAS		&   128 &  287 &  185/0 & 205 &  221 & 174/0 &  13 &  100 & 486/1 & 36 & 112 & 105/347 \\ 
LeetCode	&   856 & 1784 &   26/0 & 860 & 1785 &  21/0 & 881 & 1785 & 0/0 & 676 & 1780 &  70/140 \\ 
StringFuzz	& 504 & 295 & 264/2 & 677 & 240 & 63/85 & 265 & 187 & 609/4 & 493 & 190 & 377/5 \\ 
cvc4\textsubscript{pred}	& 16 & 814 & 5/0 & 11 & 818 & 6/0 & 12 & 808 & 15/0 & 8 & 772 & 41/14 \\ 
cvc4\textsubscript{term}	& 13 & 1030 & 2/0 & 8 & 936 & 12/89 & 5 & 2021 & 19/0 & 16 & 958 & 53/18 \\ \hline
\end{tabular}
\label{table:base_benchmark}
\end{table*}

\begin{table*}[t]
\centering
\caption{Results of z3-Trau, cvc4, and z3 on str\_int benchmark}
\begin{tabular}{l | r r r | r r r | r r r | r r r}
\hline
\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{z3-str3} \\
			& sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ \\ \hline
full\_str\_int		& 3289 & 17089 & 1195/0 & 2185 & 16377 & 3011/0 & 2716 & 16831 & 2026/0 & 422 & 16034 & 4131/986 \\ 
filtered\_str\_int	& 3281 & 2912 & 1203/0 & 2210 & 2211 & 2975/0 & 2729 & 2655 & 2012/0 & 424 & 1944 & 4106/922 \\ \hline
\end{tabular}
\label{table:str_int_benchmark}
\end{table*}

In this section, we compare our implementation z3-Trau with other SMT tools cvc4, z3, and z3-str3 as evauation. To show the general performance of z3-Trau, we compare z3-Trau with other string solvers on selected string benchmarks: PyEx is a benchmark obtained from symbolic execution of Python code[]; APLAS is a benchmark involving looping word equations[]; 
LeetCode is obtiained from concolic testing LeetCode solutions written in Python code; StringFuzz is a benchmark of instance SMT-lib string problems generated by StringFuzz generator tool[]; cvc4\textsubscript{pred} and cvc4\textsubscript{term} are benchmarks provided by the cvc4 development team[]. Table~\ref{table:base_benchmark} shows the result of the comparison. The experiments are conducted with machines of the following specifications: 4-core CPU, 8GB RAM, Ubuntu 18.4-LVM OS. We set the timeout is to 10 seconds. Because the amount of problems is very large, we ran these experiments separately on several machines with the same specification on a computer cluster. The results are either sat, unsat, timeout, or $\times$. $\times$ may be unknown, error, or exception.

>>>>

\begin{table*}[t]
\centering
\caption{Results of z3-Trau, cvc4, and z3 on string benchmarks}
\begin{tabular}{l | r r r | r r r | r r r | r r r}
\hline
\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{z3-str3} \\
			& sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ \\ \hline
PyEx		& 19586 & 3858 & 1969/8 & 19763 & 3834 & 0/1824 & 16581 & 3832 & 5008/0 & 3024 & 3839 & 16708/1850 \\ 
APLAS		&   128 &  287 &  185/0 & 205 &  221 & 174/0 &  13 &  100 & 486/1 & 38 & 111 & 93/358 \\ 
LeetCode	&   856 & 1784 &   26/0 & 860 & 1785 &  21/0 & 881 & 1785 & 0/0 & 670 & 1780 &  83/133 \\ 
StringFuzz	& 502 & 294 & 267/2 & 677 & 240 & 63/85 & 265 & 187 & 609/4 & 493 & 190 & 377/5 \\ 
cvc4\textsubscript{pred}	& 16 & 814 & 5/0 & 11 & 818 & 6/0 & 12 & 808 & 15/0 & 8 & 772 & 41/14 \\ 
cvc4\textsubscript{term}	& 13 & 1030 & 2/0 & 8 & 936 & 12/89 & 5 & 1021 & 19/0 & 16 & 958 & 53/18 \\ \hline
\end{tabular}
\label{table:base_benchmark}
\end{table*}

\begin{table*}[t]
\centering
\caption{Results of z3-Trau, cvc4, and z3 on str\_int benchmark}
\begin{tabular}{l | r r r | r r r | r r r | r r r}
\hline
\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{z3-str3} \\
			& sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ \\ \hline
full\_str\_int		& 3294 & 17088 & 1191/0 & 2185 & 16377 & 3011/0 & 422 & 16034 & 4131/986 & 2731 & 16832 & 2010/0 \\ 
filtered\_str\_int	& 3281 & 2912 & 1203/0 & 2210 & 2211 & 2975/0 & 2729 & 2655 & 2012/0 & 424 & 1944 & 4106/922 \\ \hline
\end{tabular}
\label{table:str_int_benchmark}
\end{table*}

In this section, we compare our implementation z3-Trau with other SMT tools cvc4, z3, and z3-str3 as evauation. To show the general performance of z3-Trau, we compare z3-Trau with other string solvers on selected string benchmarks: PyEx is a benchmark obtained from symbolic execution of Python code[]; APLAS is a benchmark involving looping word equations[]; 
LeetCode is obtiained from concolic testing LeetCode solutions written in Python code; StringFuzz is a benchmark of instance SMT-lib string problems generated by StringFuzz generator tool[]; cvc4\textsubscript{pred} and cvc4\textsubscript{term} are benchmarks provided by the cvc4 development team[]. Table~\ref{table:base_benchmark} shows the result of the comparison. The experiments are conducted with machines of the following specifications: 4-core CPU, 8GB RAM, Ubuntu 18.4-LVM OS. We set the timeout is to 10 seconds. Because the amount of problems is very large, we ran these experiments separately on several machines with the same specification on a computer cluster. The results are either sat, unsat, timeout, or $\times$. In case $\times$, the result may be unknown, error, or exception.
